Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-12-06 scagnostics.Rmd
Fig 2,3 with rescaled holes index.

@@

```{r plotV1V2toV3V4, fig.width=6, fig.height=7, fig.cap="PPIs for projections along an interpolation between two nuisance projections. All projections would be nuisance so the PPI are ideally low and smooth, with little difference between sample sizes (solid lines: $n=1000$; dashed: $n=100$). The scagnostic PPIs are noisy. Some indexes have distinct differences in values between sample sizes."}
fullResMelt <- fullRes %>%
  mutate(convex = 1-convex) %>% 
  gather(PPI, value, -t, -name, -size) %>%
  filter(PPI != "cmass") %>%
  mutate(PPI = fct_relevel(PPI, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
fullResMelt %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none") + xlab("Sequence of projections (t)") + ylab("PPI value")
```

@@

```{r plannedtour, fig.width=6, fig.height=7, fig.cap="PPIs for projections along an interpolation between a nuisance and a structured projection (solid lines: $n=1000$; dashed: $n=100$). Most of the indexes have peaks at the end of the sequence, indicating that they see the structure. The scagnostics, MIC and TIC see all three structures, so are more flexible for general pattern detection."}
#fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size"))
fullResMeltPlanned <- fullResPlanned %>%
  mutate(convex = 1-convex) %>% 
  gather(PPI, value, -t, -name, -size) %>%
  filter(PPI != "cmass") %>%
  mutate(PPI = fct_relevel(PPI, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
fullResMeltPlanned %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none") + xlab("Sequence of projections (t)") + ylab("PPI value")
```

@@

\textcolor{red}{The plot is not perfect. I use alpha to fade out points, but cant find value that gives nice picture here. In addition the timer isnt precise enough to resolve timing for some indexes on small datasets, they are zeroes, appear on bottom of the log10 y axis.}

>>>>

rescaleHoles <- function(x){
  if(x<0.8) x <- 0.
  else x <- (x-0.8) * 5
  return(x)
}

rescaleCmass <- function(x){
  if(x<0.2) x <- 0.
  else x <- (x-0.2) * 1.25
  return(x)
}

@@

```{r plotV1V2toV3V4, fig.width=6, fig.height=7, fig.cap="PPIs for projections along an interpolation between two nuisance projections. All projections would be nuisance so the PPI are ideally low and smooth, with little difference between sample sizes (solid lines: $n=1000$; dashed: $n=100$). The scagnostic PPIs are noisy. Some indexes have distinct differences in values between sample sizes."}
fullResMelt <- fullRes %>%
  mutate(convex = 1-convex) %>%
  rowwise() %>%
  mutate(holes = rescaleHoles(holes)) %>%
  gather(PPI, value, -t, -name, -size) %>%
  filter(PPI != "cmass") %>%
  mutate(PPI = fct_relevel(PPI, "holes", "cmass", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
fullResMelt %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none") + xlab("Sequence of projections (t)") + ylab("PPI value")
```

@@

```{r plannedtour, fig.width=6, fig.height=7, fig.cap="PPIs for projections along an interpolation between a nuisance and a structured projection (solid lines: $n=1000$; dashed: $n=100$). Most of the indexes have peaks at the end of the sequence, indicating that they see the structure. The scagnostics, MIC and TIC see all three structures, so are more flexible for general pattern detection."}
#fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size"))
fullResMeltPlanned <- fullResPlanned %>%
  mutate(convex = 1-convex) %>% 
  rowwise() %>%
  mutate(holes = rescaleHoles(holes)) %>%
  gather(PPI, value, -t, -name, -size) %>%
  filter(PPI != "cmass") %>%
  mutate(PPI = fct_relevel(PPI, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
fullResMeltPlanned %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none") + xlab("Sequence of projections (t)") + ylab("PPI value")
```

@@
